Towards Non-Consumptive Cloud Computing for Digital Humanities

### 2014-02-26 cloudpaper/paper.tex
Updates to paper

\maketitle
\begin{abstract}
As the amount of digitized archives grows, compute technology plays an increasing important role in digital humanities research. The advent of cloud computing offers researcher computation capabilities to process tens of thousands of archives which goes beyond their desktop machines can process. However, for copyrighted archives, it poses security challenges to the compute platform. In this paper, we investigate non-consumptive research, a research that allows user access copyrighted archives while prevents archives reconstruction during user access, in cloud computing. We build an infrastructure as a service (IaaS) cloud framework that makes use of data capsule to enforce non-consumptive research policy in virtual machine. This paper presents our architecture design and implementation details, and outlines next steps for future development.
\end{abstract}

% A category with the (minimum) three required fields
\category{H.3.4}{Systems and Software}{Distributed systems}[cloud computing, data capsule]
%A category including the fourth, optional field follows...
\category{K.6.m}{Miscellaneous}{Security}[non-consumptive research]

@@

\keywords{Cloud computing, Non-consumptive research, data capsule} % NOT required for Proceedings

@@

Related work of Data Capsule.

@@

@@

The system is designed to allow user to access copyrighted data in a compromised operating system which runs in a virtual machine (VM). Neither the operating system, the driver, nor the applications (except for user’s application running against HTRC Data service) are trusted. Although our system allows arbitrary behaviors in VM, it does require some trusted components. The virtual machine monitor (VMM) that runs virtual machines is part of the trusted computing base (TCB). The hosts where VMM locates are also part of the TCB. The internal network among VMs is part of the TCB, i.e., firewall policy is sufficient to prevent attack from one VM to another one. User’s application that runs against HTRC Data service is considered trustworthy, although it could potentially encode the copyrighted data and deliver it as final result. We require user to sign a legal agreement before she uses our system. We intend to add some result analysis to automatically detect data leakage and leave this as future work.

The data capsule was developed by Borders et al. \cite{Borders:2009:PCD:1855768.1855791}. It enforces two modes on a single virtual machine, i.e., maintenance mode and secure mode, to provide secure access to sensitive data. In maintenance mode, user is free to access internet and install software in VM. While in secure mode, sensitive data stored in a secure volume will be attached to the VM and become visible to user. The network access is blocked in secure mode to prevent data leakage by network. When user switches from secure mode to maintenance mode, changes made to places other than volume are wiped out so that sensitive data cannot leak through copying to local disk neither. Only changes made to volume is persistent. Therefore, in data capsule, user can access sensitive data and leakage cannot take place neither through network channel nor through disk.

>>>>

\maketitle
\begin{abstract}
As the number of digitized archives grows, computing technology is playing an
increasingly important role in digital humanities research. The advent of cloud
computing offers researchers the ability to quickly process tens of thousands
of archives, going far beyond the capabilities of their desktop machines.
However, copyrighted archives pose a crucial security challenge to this
otherwise promising computational research platform. In this paper, we
investigate \emph{non-consumptive research}, that is, research that allows
users access to copyrighted archives via cloud computing, while preventing the
release of the archive data during user access. We have built an infrastructure
as a service (IaaS) cloud framework that makes use of storage capsules to
enforce a non-consumptive research policy within a virtual machine.  This paper
presents our architecture, design, and implementation details, and outlines the
next steps for future development.
\end{abstract}

% A category with the (minimum) three required fields
\category{H.3.4}{Systems and Software}{Distributed Systems}[Cloud Computing, Storage Capsules]
%A category including the fourth, optional field follows...
\category{K.6.m}{Miscellaneous}{Security}[Non-consumptive Research]

@@

\keywords{Cloud computing, Non-consumptive Research, Storage Capsules} % NOT required for Proceedings

@@

Storage Capsules \cite{Borders:2009:PCD:1855768.1855791} is a mechanism for
containing sensitive data within a virtualized environment with the goal of
minimizing the available channels to leak that data.  Although Capsules
provides no guarantees on the integrity of the stored data -- which could be
modified or deleted by an attacker -- this poses little issue when Capsules is
applied to non-consumptive research, where the copyrighted source data can
simply be made read-only.  Capsules uses virtual machine snapshotting and
simple policy-based restriction mechanisms to allow a user to enter a
restricted ``secure'' mode, where network and other data channels are
restricted in exchange for access to the data being protected.  After using the
protected data, when the user returns to normal use of the system, all changes
to the system except those made to the designated secure data are forgotten,
and the system returns to the state it was in before the switch to secure mode.
This use model is readily applicable to non-consumptive research, in that a
researcher can administer their system (e.g. install any required software
tools) and then switch to ``secure'' mode to perform their analysis.

@@

Storage Capsules was developed by Borders et al.
\cite{Borders:2009:PCD:1855768.1855791}. It enforces two modes on a single
virtual machine, i.e., maintenance mode and secure mode, to provide secure
access to sensitive data. In maintenance mode, user is free to access internet
and install software in VM. While in secure mode, sensitive data stored in a
secure volume will be attached to the VM and become visible to user. The
network access is blocked in secure mode to prevent data leakage by network.
When user switches from secure mode to maintenance mode, changes made to places
other than volume are wiped out so that sensitive data cannot leak through
copying to local disk neither. Only changes made to volume is persistent.
Therefore, in data capsule, user can access sensitive data and leakage cannot
take place neither through network channel nor through disk.

@@

The system is designed to allow users to access copyrighted data in a potentially
compromised operating system which runs in a virtual machine (VM). Neither the
operating system, the driver, nor the applications (except for user’s
application running against HTRC Data service) are trusted. Although our system
allows arbitrary behaviors in VM, it does require some trusted components. The
virtual machine monitor (VMM) that runs virtual machines is part of the trusted
computing base (TCB). The hosts where VMM locates are also part of the TCB. The
internal network among VMs is part of the TCB, i.e., firewall policy is
sufficient to prevent attack from one VM to another one. User’s application
that runs against HTRC Data service is considered trustworthy, although it
could potentially encode the copyrighted data and deliver it as final result.
We require user to sign a legal agreement before she uses our system. We intend
to add some result analysis to automatically detect data leakage and leave this
as future work.
